\judul

### 2025-04-24 article/article.tex
shrink matplotlib pgf to graph size, change library name for comparison method to computational method used, add full stop to captions, add psuedocode for training, change figure placement to hbp to reduce dead whitespace.

\section{Methods}
This section describes the proposed method and the case studies we used.
\subsection{SpectralSVR}
% Model design
The design of the proposed model is built upon performing regression in the Fourier domain. This means that any function values that will be used by the model, should be transformed into their coefficients. And, any predictions from the model, which are coefficients, should be transformed back into function values. The training process is shown in \lccref{fig:spectralsvr_training}. The process starts with determining the feature and label functions. Typically, the feature functions would include the forcing term and other parameter functions such as the solution at the current time step. The label functions typically is the solution function or the solution function at the next time step. The Fourier coefficients are then computed using the DFT\@. The coefficients are then flattened for each sample. A scaling function is fitted on the flattened feature coefficients and the feature coefficients are then scaled using the fitted scaling function. Finally, Using the scaled feature and label coefficients, the training function computes the parameters of the model.

\begin{figure}[H]
  \centering
  \tikzfig{figures/training_spectralsvr}
  \caption{SpectralSVR training diagram}\label{fig:spectralsvr_training}
\end{figure}
% TODO: add psuedocode for training the model
% TODO: add figures of how a dataset of 1D functions is represented and the transformed coefficient representation

The prediction process is shown in \lccref{fig:spectralsvr_prediction}. The process starts by transforming the feature functions into their coefficients with the DFT\@. These coefficients are then scaled with the scaling function fitted during training. The scaled feature coefficients are then used with the learned parameters to produce the predicted coefficients using the LSSVR prediction function. Finally, the inverse DFT is computed on the predicted coefficients to obtain the predicted function value.
\begin{figure}[H]
  \centering
  \tikzfig{figures/prediction_spectralsvr}
  \caption{SpectralSVR prediction diagram}\label{fig:spectralsvr_prediction}
\end{figure}

To interpret the relationship learned by the LSSVR between the feature and label coefficients, we use two tools called the correlation image and p-matrix introduced by \citet{ustunVisualisationInterpretationSupport2007}.

@@

Next, we have the correlation image and p-matrix for the model of each noise level. The results are shown in \lccref{fig:scenario_1_interpretation}. Each row in the figure represent the results of a model trained on a different noise level. The correlation image for 5\% and 10\% noise show clear lines on the coefficient corresponding to the output coefficient that was sorted. We can also see that the negative wave number reflection also being sorted. This is because of the reflection that occurs with complex Fourier coefficients for real-valued functions. There are other faint vertical lines you are able to see for other input coefficients. These faint lines are not sorted like the corresponding coefficients we mentioned before. Meaning, while they don't affect the particular output coefficients that were sorted, they do show that there is information embedded in the kernel matrix for these input coefficients. However, if we look at the 50\% noise correlation image, even the corresponding coefficient does not show a clear line or gradient. The lines are more noisy compared to the other noise levels. But the kernel still manages to embed some information. The p-matrices show that the model itself is able to still learn some relationship between the input coefficients and the output coefficients. For the 5\% and 10\% noise levels, the p-matrices show very clearly the contributions of input coefficients to the output coefficients. However, looking at the p-matrix for 50\% noise level, the lower wave numbers show lower contribution of input coefficients to the output coefficients.
\begin{figure}[H]
  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
    \centering
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_ci_5.pgf}
      \end{adjustbox}
      \caption{Correlation image 5\% noise.}\label{fig:sc1_ci_5}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_pm_5.pgf}
      \end{adjustbox}
      \caption{The p-matrix for 5\% noise.}\label{fig:sc1_pm_5}
    \end{subfigure}
    % \\[\baselineskip]
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_ci_10.pgf}
      \end{adjustbox}
      \caption{Correlation image 10\% noise.}\label{fig:sc1_ci_10}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_pm_10.pgf}
      \end{adjustbox}
      \caption{The p-matrix for 10\% noise.}\label{fig:sc1_pm_10}
    \end{subfigure}
    % \\[\baselineskip]
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_ci_50.pgf}
      \end{adjustbox}
      \caption{Correlation image 50\% noise.}\label{fig:sc1_ci_50}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_pm_50.pgf}
      \end{adjustbox}
      \caption{The p-matrix for 50\% noise.}\label{fig:sc1_pm_50}
    \end{subfigure}
  \end{adjustwidth}
  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row). The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_1_interpretation}
\end{figure}

@@

The testing results are complimented with a rollout experiment. The results from the rollout are shown in \lccref{fig:scenario_2_rollout}. The rollout starts from time \(t=0\). In all the plots, this is at the bottom. We have included this initial condition in the plots. From this initial condition in combination with the forcing term at the initial time step, the model predicts the first time step solution. The model then uses the predicted solution combined with the corresponding forcing term to predict the second time step. To see how well the model is performing relative to the actual target values, we compute the difference between the two as shown in \lccrefs{fig:sc2_rollout_diff_0.0,fig:sc2_rollout_diff_0.01,fig:sc2_rollout_diff_0.1}. Observe that errors are introduced relatively early around time \(t=1\). However, the model rollout stays stable until the end despite this error. This results in the model being able to finish the rollout for this sample.
\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_target_0.0.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_rollout_target_0.0}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_pred_0.0.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_rollout_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_diff_0.0.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_rollout_diff_0.0}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_target_0.01.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_rollout_target_0.01}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_pred_0.01.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_rollout_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_diff_0.01.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_rollout_diff_0.01}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_target_0.1.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_rollout_target_0.1}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_pred_0.1.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_rollout_pred_0.1}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_diff_0.1.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_rollout_diff_0.1}
    \end{subfigure}
    % \\[0.7\baselineskip]
  \end{adjustwidth}
  \caption{The rollout predictions for one of the test function. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_rollout}
\end{figure}

@@

The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value. The discrete Fourier transform of the values are then used for doing rollout with the model. For the forcing term, we just use a constant function with a value of zero. The rollout predictions are shown in \lccref{fig:scenario_2_exact}. The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\). Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions. For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction. The error stays to about half the maximum function value. We do see some more noticeable error in the flatter parts of the function. The error also take a very similar shape across the different viscosity values. Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples. The error for the flatter functions may also be alleviated by including similar flatter functions during training.
\begin{figure}[H]
  \centering
  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.0.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.0\)}\label{fig:sc2_exact_target_0.0}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.0.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.0\)}\label{fig:sc2_exact_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.0.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.0\)}\label{fig:sc2_exact_diff_0.0}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.01.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.01\)}\label{fig:sc2_exact_target_0.01}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.01.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.01\)}\label{fig:sc2_exact_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.01.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.01\)}\label{fig:sc2_exact_diff_0.01}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.1.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.1\)}\label{fig:sc2_exact_target_0.1}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.1.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.1\)}\label{fig:sc2_exact_pred_0.1}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.1.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.1\)}\label{fig:sc2_exact_diff_0.1}
    \end{subfigure}
    % \\[0.7\baselineskip]
  \end{adjustwidth}
  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
\end{figure}

The correlation image and p-matrix for each viscosity can be seen in \lccref{fig:scenario_2_interpretation}. Analyzing the correlation images first, we see that some columns are sorted in correlation to how the samples are sorted based on the real component of the 4th output wave number. For the inviscid equation, this correlation is the strongest with multiple columns exhibiting the correlation. The highest and visually most sorted values are from the forcing term portion of the inputs. Different wave numbers in the inputs are also sorted differently, this indicates an inverse correlation. For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_ci_0.0.pgf}
    \end{adjustbox}
    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_pm_0.0.pgf}
    \end{adjustbox}
    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
  \end{subfigure}
  % \\[-0.7\baselineskip]
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_ci_0.01.pgf}
    \end{adjustbox}
    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_pm_0.01.pgf}
    \end{adjustbox}
    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
  \end{subfigure}
  % \\[-0.7\baselineskip]
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_ci_0.1.pgf}
    \end{adjustbox}
    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \begin{adjustbox}{width=\linewidth}
      \input{figures/burgers_pm_0.1.pgf}
    \end{adjustbox}
    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
  \end{subfigure}
  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different viscosity (row). The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
\end{figure}

@@

\input{apendix.tex}

\bibliographystyle{elsarticle-harv}
\bibliography{references.bib}
\end{document}

>>>>

\section{Methods}
This section describes the proposed method and the case studies we used.
\subsection{SpectralSVR}
% Model design
The design of the proposed model is built upon performing regression in the Fourier domain. This means that any function values that will be used by the model, should be transformed into their coefficients. And, any predictions from the model, which are coefficients, should be transformed back into function values.
\begin{figure}[hbp]
  \centering
  \tikzfig{figures/training_spectralsvr}
  \caption{SpectralSVR training diagram.}\label{fig:spectralsvr_training}
\end{figure}

The training process is shown in \lccref{fig:spectralsvr_training}. The process in psuedocode is also shown in \lccref{alg:spectralsvr_training_psuedocode}. The process starts with determining the parameter and solution functions. Typically, the parameter functions would include the forcing term and others such as the initial solution function values. The solution function typically is the state variable that the PDE constraints using its derivatives, such as the displacement of a membrane for the wave equation. Next, the features and labels are constructed. Generally, the Fourier coefficients for both functions are computed using the DFT\@. And then, the parameter and solution coefficients are used as the feature and labels respectively. To finalize the construction, the coefficients are flattened into one dimension for each sample. And then, the features are scaled for training the LSSVR\@. Finally, after the feature and label construction, we train the LSSVR by computing the parameters of the model. In the psuedocode this starts by computing the kernel matrix from the features. And then the two matrices, \(\vb{A}\) and \(\vb{B}\), are put together to compute the model parameters via least-squares, which marks the end of the training process.
\begin{algorithm}[hbp]
  \caption{SpectralSVR Training Psuedocode.}\label{alg:spectralsvr_training_psuedocode}
  \begin{algorithmic}[1]
    \Procedure{TrainSpectralSVR}{$\vb{U}, \vb{F}, C $}
    \State{\(\vb{\hat{U}} \gets DFT(\vb{U})\)}
    \State{\(\vb{\hat{F}} \gets DFT(\vb{F})\)}
    \Comment{Compute Fourier coefficients of training functions}
    \State{\(\vb{X} \gets finalizeFeatures(\vb{\hat{U}},\vb{\hat{F}})\)}
    \State{\(\vb{y} \gets finalizeLabels(\vb{\hat{U}},\vb{\hat{F}})\)}
    \State{\(\Omega \gets K(\vb{X})\)}
    \Comment{Construct matrix of inner products}
    \State{\(\vb{A} \gets [[]]\)}
    \State{\(\vb{B} \gets [[]]\)}
    \State{\(\vb{A}[1:,1:] \gets \Omega+\frac{\vb{I}}{C}, \vb{A}[0,:] \gets 0,\vb{A}[:,0] \gets 0\)}
    \State{\(\vb{B}[0] \gets 0, \vb{B}[1:] \gets \vb{y}\)}
    \State{\(\vb{S} \gets leastSquares(\vb{A},\vb{B})\)}
    \State{\(\vb{\alpha} \gets \vb{S}[1:],\vb{b} \gets \vb{S}[0]\)}
    \Comment{Learned model parameters}
    \State{\textbf{return} \(\vb{\alpha}, \vb{b}\)}
    \EndProcedure{}
  \end{algorithmic}
\end{algorithm}

% TODO: add figures of how a dataset of 1D functions is represented and the transformed coefficient representation
% The data transformations are visualized in \lccref{fig:spectralsvr_training_data}.
% \begin{figure}[hbp]
%   \centering
%   \tikzfig{figures/training_spectralsvr_data}
%   \caption{SpectralSVR training data transformations.}\label{fig:spectralsvr_training_data}
% \end{figure}

The prediction process is shown in \lccref{fig:spectralsvr_prediction}. The process starts by transforming the feature functions into their coefficients with the DFT\@. These coefficients are then scaled with the scaling function fitted during training. The scaled feature coefficients are then used with the learned parameters to produce the predicted coefficients using the LSSVR prediction function. Finally, the inverse DFT is computed on the predicted coefficients to obtain the predicted function value.
\begin{figure}[hbp]
  \centering
  \tikzfig{figures/prediction_spectralsvr}
  \caption{SpectralSVR prediction diagram.}\label{fig:spectralsvr_prediction}
\end{figure}

@@

Next, we have the correlation image and p-matrix for the model of each noise level. The results are shown in \lccref{fig:scenario_1_interpretation}. Each row in the figure represent the results of a model trained on a different noise level. The correlation image for 5\% and 10\% noise show clear lines on the coefficient corresponding to the output coefficient that was sorted. We can also see that the negative wave number reflection also being sorted. This is because of the reflection that occurs with complex Fourier coefficients for real-valued functions. There are other faint vertical lines you are able to see for other input coefficients. These faint lines are not sorted like the corresponding coefficients we mentioned before. Meaning, while they don't affect the particular output coefficients that were sorted, they do show that there is information embedded in the kernel matrix for these input coefficients. However, if we look at the 50\% noise correlation image, even the corresponding coefficient does not show a clear line or gradient. The lines are more noisy compared to the other noise levels. But the kernel still manages to embed some information. The p-matrices show that the model itself is able to still learn some relationship between the input coefficients and the output coefficients. For the 5\% and 10\% noise levels, the p-matrices show very clearly the contributions of input coefficients to the output coefficients. However, looking at the p-matrix for 50\% noise level, the lower wave numbers show lower contribution of input coefficients to the output coefficients.
\begin{figure}[hbp]
  \begin{adjustwidth}{-0.05\linewidth}{-0.05\linewidth}
    \centering
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_ci_5.pgf}
      \end{adjustbox}
      \caption{Correlation image 5\% noise.}\label{fig:sc1_ci_5}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_pm_5.pgf}
      \end{adjustbox}
      \caption{The p-matrix for 5\% noise.}\label{fig:sc1_pm_5}
    \end{subfigure}
    % \\[\baselineskip]
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_ci_10.pgf}
      \end{adjustbox}
      \caption{Correlation image 10\% noise.}\label{fig:sc1_ci_10}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_pm_10.pgf}
      \end{adjustbox}
      \caption{The p-matrix for 10\% noise.}\label{fig:sc1_pm_10}
    \end{subfigure}
    % \\[\baselineskip]
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_ci_50.pgf}
      \end{adjustbox}
      \caption{Correlation image 50\% noise.}\label{fig:sc1_ci_50}
    \end{subfigure}
    \begin{subfigure}{0.49\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/antiderivative_pm_50.pgf}
      \end{adjustbox}
      \caption{The p-matrix for 50\% noise.}\label{fig:sc1_pm_50}
    \end{subfigure}
  \end{adjustwidth}
  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different noise level (row). The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_1_interpretation}
\end{figure}

@@

The testing results are complimented with a rollout experiment. The results from the rollout are shown in \lccref{fig:scenario_2_rollout}. The rollout starts from time \(t=0\). In all the plots, this is at the bottom. We have included this initial condition in the plots. From this initial condition in combination with the forcing term at the initial time step, the model predicts the first time step solution. The model then uses the predicted solution combined with the corresponding forcing term to predict the second time step. To see how well the model is performing relative to the actual target values, we compute the difference between the two as shown in \lccrefs{fig:sc2_rollout_diff_0.0,fig:sc2_rollout_diff_0.01,fig:sc2_rollout_diff_0.1}. Observe that errors are introduced relatively early around time \(t=1\). However, the model rollout stays stable until the end despite this error. This results in the model being able to finish the rollout for this sample.
\begin{figure}[hbp]
  \centering
  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_target_0.0.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.0\).}\label{fig:sc2_rollout_target_0.0}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_pred_0.0.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.0\).}\label{fig:sc2_rollout_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_diff_0.0.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.0\).}\label{fig:sc2_rollout_diff_0.0}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_target_0.01.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.01\).}\label{fig:sc2_rollout_target_0.01}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_pred_0.01.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.01\).}\label{fig:sc2_rollout_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_diff_0.01.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.01\).}\label{fig:sc2_rollout_diff_0.01}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_target_0.1.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.1\).}\label{fig:sc2_rollout_target_0.1}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_pred_0.1.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.1\).}\label{fig:sc2_rollout_pred_0.1}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_rollout_diff_0.1.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.1\).}\label{fig:sc2_rollout_diff_0.1}
    \end{subfigure}
    % \\[0.7\baselineskip]
  \end{adjustwidth}
  \caption{The rollout predictions for one of the test function. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_rollout}
\end{figure}

@@

The exact function \cref{eq:burgers_exact_solution} is computed for each viscosity value. The discrete Fourier transform of the values are then used for doing rollout with the model. For the forcing term, we just use a constant function with a value of zero. The rollout predictions are shown in \lccref{fig:scenario_2_exact}. The model is not successful in the rollout for the inviscid equation and for the viscosity of \(\nu=0.01\). Both of these cases, the model produces too much error that the original function is no longer recognizable in the predictions. For the higher viscosity value of \(\nu=0.1\) the rollout produces a recognizable prediction. The error stays to about half the maximum function value. We do see some more noticeable error in the flatter parts of the function. The error also take a very similar shape across the different viscosity values. Since we essentially used the same solutions for training the model for each viscosity, the similarity in error means that it can be alleviated with more diverse training samples. The error for the flatter functions may also be alleviated by including similar flatter functions during training.
\begin{figure}[hbp]
  \centering
  \begin{adjustwidth}{-0.1\linewidth}{-0.1\linewidth}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.0.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.0\).}\label{fig:sc2_exact_target_0.0}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.0.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.0\).}\label{fig:sc2_exact_pred_0.0}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.0.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.0\).}\label{fig:sc2_exact_diff_0.0}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.01.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.01\).}\label{fig:sc2_exact_target_0.01}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.01.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.01\).}\label{fig:sc2_exact_pred_0.01}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.01.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.01\).}\label{fig:sc2_exact_diff_0.01}
    \end{subfigure}
    \\[0.7\baselineskip]
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_target_0.1.pgf}
      \end{adjustbox}
      \caption{The target for \(\nu=0.1\).}\label{fig:sc2_exact_target_0.1}
    \end{subfigure}
    \begin{subfigure}{0.33\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_pred_0.1.pgf}
      \end{adjustbox}
      \caption{The prediction for \(\nu=0.1\).}\label{fig:sc2_exact_pred_0.1}
    \end{subfigure}
    \begin{subfigure}{0.32\linewidth}
      \begin{adjustbox}{width=\linewidth}
        \input{figures/burgers_exact_diff_0.1.pgf}
      \end{adjustbox}
      \caption{The difference for \(\nu=0.1\).}\label{fig:sc2_exact_diff_0.1}
    \end{subfigure}
    % \\[0.7\baselineskip]
  \end{adjustwidth}
  \caption{The rollout predictions for one of the exact function in \lccref{eq:burgers_exact_solution}. The difference is calculated as the targets subtracted by the predictions.}\label{fig:scenario_2_exact}
\end{figure}

The correlation image and p-matrix for each viscosity can be seen in \lccref{fig:scenario_2_interpretation}. Analyzing the correlation images first, we see that some columns are sorted in correlation to how the samples are sorted based on the real component of the 4th output wave number. For the inviscid equation, this correlation is the strongest with multiple columns exhibiting the correlation. The highest and visually most sorted values are from the forcing term portion of the inputs. Different wave numbers in the inputs are also sorted differently, this indicates an inverse correlation. For a higher viscosity of \(\nu=0.01\), a weaker correlation is still present.
\begin{figure}[hbp]
  \centering
  \begin{subfigure}{0.49\linewidth}
    \centering
    \begin{adjustbox}{height=5.5cm}
      \input{figures/burgers_ci_0.0.pgf}
    \end{adjustbox}
    \caption{Correlation image \(\nu=0.0\).}\label{fig:sc2_ci_0.0}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \centering
    \begin{adjustbox}{height=5.5cm}
      \input{figures/burgers_pm_0.0.pgf}
    \end{adjustbox}
    \caption{The p-matrix for \(\nu=0.0\).}\label{fig:sc2_pm_0.0}
  \end{subfigure}
  % \\[-0.7\baselineskip]
  \begin{subfigure}{0.49\linewidth}
    \centering
    \begin{adjustbox}{height=5.5cm}
      \input{figures/burgers_ci_0.01.pgf}
    \end{adjustbox}
    \caption{Correlation image \(\nu=0.01\).}\label{fig:sc2_ci_0.01}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \centering
    \begin{adjustbox}{height=5.5cm}
      \input{figures/burgers_pm_0.01.pgf}
    \end{adjustbox}
    \caption{The p-matrix for \(\nu=0.01\).}\label{fig:sc2_pm_0.01}
  \end{subfigure}
  % \\[-0.7\baselineskip]
  \begin{subfigure}{0.49\linewidth}
    \centering
    \begin{adjustbox}{height=5.5cm}
      \input{figures/burgers_ci_0.1.pgf}
    \end{adjustbox}
    \caption{Correlation image \(\nu=0.1\).}\label{fig:sc2_ci_0.1}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
    \centering
    \begin{adjustbox}{height=5.5cm}
      \input{figures/burgers_pm_0.1.pgf}
    \end{adjustbox}
    \caption{The p-matrix for \(\nu=0.1\).}\label{fig:sc2_pm_0.1}
  \end{subfigure}
  \caption{Correlation image (left column) and p-matrix (right column) for each model trained on a different viscosity (row). The correlation image was sorted same order the values of the real component of wave number \(k=2\) were sorted in descending order.}\label{fig:scenario_2_interpretation}
\end{figure}

@@

\bibliographystyle{elsarticle-harv}
\bibliography{references.bib}

\input{apendix.tex}
\end{document}
